Minicaml, a purely functional, didactical programming language\\WORK IN PROGRESS DRAFT

### 2020-01-07 paper/paper.tex
makefile
paper and opam spec
operational semantics in paper

@@

@@

\section{Evaluation}

>>>>

\newcommand{\te}[1]{\text{#1}}

@@

Boolean operations are reduced using laws from the propositional calculus, such as DeMorgan's law, complement, absorption and other trivial ones.

@@

\section{Evaluation}
\subsection{Operational Semantics}

\textbf{Dictionaries}\\
Note that the evaluation step of the dictionary is considered implicit.

\begin{gather*}
	\te{Insertion} \\
	\hline \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow
	\te{true}}{<\te{env, insert k v dict}> \Rightarrow \te{dict} \cup (\te{k,v})} \\ \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, insert k v dict}> \Rightarrow \te{dict}} \\ \\
	\te{Deletion} \\ \hline \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{true}}{<\te{env, remove k dict}> \Rightarrow \te{dict} \textbackslash \{(\te{k,v})\}} \\ \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, remove k dict}> \Rightarrow \te{error}} \\ \\
	\te{Contains key} \\ \hline \\
	<\te{env}, \te{haskey k dict}> \Rightarrow \te{k} \in \te{dict} \\ \\
	\te{Retreive a value} \\ \hline \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{true}}{<\te{env, getkey k dict}> \Rightarrow \te{v}} \\ \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, getkey k dict}> \Rightarrow \te{error}} \\ \\
	\te{Filter by keys} \\ \hline \\
	\dfrac{<\te{env, ks}> \Rightarrow \te{\{k1, ..., kn\}}}{<\te{env, filterkeys ks d}> \Rightarrow \{ (k, v) \in \te{d} \mid (k \in ks) \}} \\ \\
	\te{Map} \\ \hline \\
	\dfrac{<\te{env, f}> \Rightarrow \lambda(x)}{<\te{env, map f d}> \Rightarrow \{ (k, \lambda(v)) \mid (k, v) \in \te{d}  \}} \\ \\
	\te{Fold Left} \\ \hline \\
	\dfrac{\begin{aligned}
		<\te{env, f}> \Rightarrow \lambda(x,y)  \\
		<\te{env, d}> \Rightarrow \{(k_1, v_1), \hdots, (k_n, v_n)\}
	\end{aligned}}{<\te{env, foldl f a d}> \Rightarrow \lambda( \hdots \lambda(\lambda(a, v_1), v_2), \hdots, v_n)} \\ \\
\end{gather*}
